Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-01-25 paper/main.tex
Updates paper

To tackle these issues with CI based testing, we take inspiration from
\emph{modification indices} in specification search. The modification indices
method tries to identify and rank changes in the model such that modifications
that improve the model fit the most are ranked higher.This ranking allows
researchers to focus first on the suggestions that can improve the model the
most and while integrating their expertise to choose the most optimal
modifications. Analogous to this, in this paper we develop a measure for
partial association for mixed data that allows us to rank the CI violations.
Additionally, this measure of conditional association also allows us tackle
other issues with CI based testing outlined in the previous paragraphs.

>>>>

There has been work on trying to come up with a single test to combine all
these test to give a single answer \citep{Eulig2023, Shipley2000}. However,
what is missing is the guide on how to how to fix these tests. To tackle these
issues with CI based testing, we take inspiration from \emph{modification
indices} in specification search. The modification indices method tries to
identify and rank changes in the model such that modifications that improve the
model fit the most are ranked higher.This ranking allows researchers to focus
first on the suggestions that can improve the model the most and while
integrating their expertise to choose the most optimal modifications. Analogous
to this, in this paper we develop a measure for partial association for mixed
data that allows us to rank the CI violations. Additionally, this measure of
conditional association also allows us tackle other issues with CI based
testing outlined in the previous paragraphs.
